\texttt Design date

### 2017-04-13 latex/secretkeybasedpublickeyencryption/paper.tex
added rsareuse idea

Lattices are also very attractive because they offer homomorphic properties, which is another of the most important topics in cryptography at the moment. This property is also extremely important because it allows for the simple construction of public key encryption schemes and key exchange shemes from secret key ciphers. We present such a scheme in this paper, as well as a homomorphic cipher suitable for instantiating the scheme.

>>>>

Lattices are also very attractive because they offer homomorphic properties, which is another of the most important topics in cryptography at the moment. This property is also extremely important because it allows for the construction of simple public key encryption schemes and key exchange shemes from secret key ciphers. We present such a scheme in this paper, as well as a homomorphic cipher suitable for instantiating the scheme.
